---
title: "ELPASO"
author: "Kelly"
date: "3/2/2021"
output: html_document
---

```{r,echo=FALSE,warning=FALSE,message=FALSE}

#library(osmdata)
library(sf)
library(tidyverse)
library(ggmap)

library(rgdal)
library(leaflet)
library(tidyverse)
library(rgeos)
library(raster)
library(ggplot2)
library(sf)
library(mapview)
library(maptools)
library(sp)
library(readxl)
library(readr)
library(grid)
library(gridExtra)
library(xtable)
library(knitr)
library(plyr)

```



```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
el_paso <- readOGR(dsn = gdb_path,layer="Elpaso_grid", verbose = FALSE)
#Transform to long/lat
el_paso <- spTransform(el_paso, "+init=epsg:4326")
#leaflet(el_paso) %>% addTiles() %>% addPolygons()

```


```{r,echo=FALSE,warning=FALSE,message=FALSE}

dir_path <- "C://Users//Kyriaki Kokka//Desktop"
df <- read_csv(paste0(dir_path, "//elpaso_2000sampled_locations.csv"))

leaflet(el_paso) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng = df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)
```


```{r}
dir_path <- "C://Users//Kyriaki Kokka//Desktop"
df <- read_csv(paste0(dir_path, "//Elpaso_2000sampled_folders.csv"))

#df <- df[,c(1,2)]
#df <- unique(df)
dfc <- df[,3]
dfc <- unique(dfc)

leaflet(el_paso) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng = df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)
```



```{r}
leaflet(el_paso) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =-106.3255827028704 , lat = 31.99858724323899, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)
```


```{r}
dir_path <- "C://Users//Kyriaki Kokka//Desktop"
df <- read_excel(paste0(dir_path, "//Telaviv_YOLOv4.xlsx"))
df1 <- df[,c(1)]
df1<- na.omit(df1)
df1 <- data.frame(str_split_fixed(df1$name, "_", 5))

df1 <- df1[,c(1,2)]
options(digits=16)
df1 <- unique(df1)
df1$X1 <- as.numeric(df1$X1)
df1$X2 <- as.numeric(df1$X2)

df <- df[,-c(1:3,6,7)]
df <- na.omit(df)
df <- unique(df)
gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Tel Aviv_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)
```

```{r}
df <- read_csv(paste0(dir_path, "//Telaviv_2000sampled_folders.csv"))
#df <- read_csv(paste0(dir_path, "//Telaviv_final_locations.csv"))

df <- df[,c(1,2)]
df <- unique(df)
dfc <- df[,3]
dfc <- unique(dfc)

a <- read_excel(paste0(dir_path, "//b.xlsx"))
a <- unique(a)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =a$lon , lat = a$lat, color = "red" , radius = 4, stroke = FALSE, fillOpacity = 0.5)
```

ROME

```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
rome <- readOGR(dsn = gdb_path,layer="Rome_grid", verbose = FALSE)
#Transform to long/lat
rome <- spTransform(rome, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//"
df <- read_csv(paste0(dir_path, "Rome_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(rome) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```

EL PASO

```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
elpaso <- readOGR(dsn = gdb_path,layer="Elpaso_grid", verbose = FALSE)
#Transform to long/lat
elpaso <- spTransform(elpaso, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//"
df <- read_csv(paste0(dir_path, "Elpaso_final_locations.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

dfc <- df[,1]
dfc <- unique(dfc)

write.csv(dfc, file = paste0(dir_path, "/Elpaso_final_folders.csv"),row.names=FALSE)

leaflet(elpaso) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```


```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
portland <- readOGR(dsn = gdb_path,layer="Portland_grid", verbose = FALSE)
#Transform to long/lat
portland <- spTransform(portland, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//"
df <- read_csv(paste0(dir_path, "Portland_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(portland) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```

San Francisco


```{r,echo=FALSE,warning=FALSE,message=FALSE}
gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="San Francisco_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

city <- readOGR(dsn = gdb_path,layer="San Jose_grid_Up", verbose = FALSE)
leaflet(city) %>% addTiles() %>% addPolygons()

a <- city@data

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "SanFrancisco_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```


Boston


```{r,echo=FALSE,warning=FALSE,message=FALSE}
gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Boston_grid_Focused", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_excel(paste0(dir_path, "boston_bad.xlsx"))
df <- unique(df)

#dfc <- df[,3]
#dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 5, stroke = FALSE, fillOpacity = 0.5)

#42.34974907886853,-71.07140441119998
leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng = -71.07140441119998 , lat = 42.34974907886853, color = "red" , radius = 5, stroke = FALSE, fillOpacity = 0.5)
```


Richmond

```{r,echo=FALSE,warning=FALSE,message=FALSE}
gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Richmond_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Richmond_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```


Buffalo


```{r,echo=FALSE,warning=FALSE,message=FALSE}
gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Buffalo_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Buffalo_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```


Bonn


```{r,echo=FALSE,warning=FALSE,message=FALSE}
gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Bonn_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Bonn_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```


Kampala


```{r,echo=FALSE,warning=FALSE,message=FALSE}
gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Kampala_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Kampala_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```

Los Angeles


```{r,echo=FALSE,warning=FALSE,message=FALSE}
gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Los Angeles_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "LosAngeles_A500sampled_folders.csv"))

# <- df[,3]
#dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```


Hamburg

```{r,echo=FALSE,warning=FALSE,message=FALSE}
gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Hamburg_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Hamburg_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```


Minneapolis


```{r,echo=FALSE,warning=FALSE,message=FALSE}
gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Minneapolis_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Minneapolis_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```


Bogota


```{r,echo=FALSE,warning=FALSE,message=FALSE}
gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Bogota_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities//"
#df <- read_csv(paste0(dir_path, "Bogota_2000sampled_folders.csv"))
#df <- read_excel(paste0(dir_path, "Bogota_motors.xlsx"))
df <- read_csv(paste0(dir_path, "BogotaImagesA_PRO2_motors.csv"))
df <- read_csv(paste0(dir_path, "BogotaImagesA_PRO2_pedals.csv"))
df <- read_excel(paste0(dir_path, "Bogota_pedals.xlsx"))


dfc <- df[,3]
df <- unique(df)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```


```{r,echo=FALSE,warning=FALSE,message=FALSE}
gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Cambridge_Mass_CityBoundary", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")
leaflet(city) %>% addTiles() %>% addPolygons()

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "CambridgeMass_A700sampled_folders.csv"))

df <- read_excel(paste0(dir_path, "Cambridge_pedals.xlsx"))
df <- unique(df)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)



```


Nantes


```{r,echo=FALSE,warning=FALSE,message=FALSE}
gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Nantes_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Nantes_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```



Frankfurt

```{r,echo=FALSE,warning=FALSE,message=FALSE}
gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Frankfurt_grids", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Frankfurt_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```


Ghent


```{r,echo=FALSE,warning=FALSE,message=FALSE}
gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Ghent_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Ghent_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```



Salt Lake City


```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Salt Lake City_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "SaltLakeCity_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)


```


San Jose


```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="San Jose_grid_Up", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "SanJose_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)
```


Barcelona

```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Barcelona_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Barcelona_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)
```


Brussels


```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Brussels_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Brussels_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)
```


Hong Kong

```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Hong Kong_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "HongKong_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)
```


Sofia


```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Sofia_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Sofia_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)
```

WashingtonDC

```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Washington_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Washington_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)
```

Cleveland

```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Cleveland_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Cleveland_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)
```

Seattle

```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Seattle_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Seattle_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)
```

Belgrade

```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Belgrade_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Belgrade_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)
```

Johannesburg

```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Johannesburg_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Johannesburg_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```


Fresno


```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Fresno_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Fresno_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```


Baltimore


```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Baltimore_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Baltimore_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```


Bucharest


```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Bucharest_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Bucharest_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```


Madrid


```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Madrid_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Madrid_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```

Warsaw

```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Warsaw_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Warsaw_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```


Tampa


```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Tampa_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Tampa_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)

```

Mexico City

```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="MexicoCity_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "MexicoCity_final_locations.csv"))

dfc <- df[,2:3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)
```


Tokyo

```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Tokyo_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Tokyo_2000sampled_folders.csv"))
df <- read_csv(paste0(dir_path, "Tokyo_final_locations.csv"))

dfc <- df[,1:2]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)
```

Paris

```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Paris_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Paris_2000sampled_folders.csv"))
#df <- read_csv(paste0(dir_path, "Paris_final_locations.csv"))
#dfc <- df[,2:3]
#dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)
```

Montreal

```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Montreal_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Montreal_2000sampled_folders.csv"))


leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)
```



Chicago

```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Chicago_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Chicago_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)


```

Dallas


```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Dallas_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Dallas_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)


```

London

```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="London_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "London_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)


```

Gothenburg

```{r,echo=FALSE,warning=FALSE,message=FALSE}

gdb_path <- "C://Users//Kyriaki Kokka//Desktop//CityGrids"
city <- readOGR(dsn = gdb_path,layer="Gothenburg_grid", verbose = FALSE)
#Transform to long/lat
city <- spTransform(city, "+init=epsg:4326")

dir_path <- "C://Users//Kyriaki Kokka//Desktop//CSV_clean_cities/"
df <- read_csv(paste0(dir_path, "Gothenburg_2000sampled_folders.csv"))

dfc <- df[,3]
dfc <- unique(dfc)

leaflet(city) %>% addTiles() %>% addPolygons() %>% addCircleMarkers(lng =df$lon , lat = df$lat, color = "red" , radius = 2, stroke = FALSE, fillOpacity = 0.5)


```

